Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-15 src/article.tex
Revise remainder of manuscript

\remove{Scaffolder was designed to be as simple to use and, assuming the Ruby
and RubyGems software are present, can be installed in a single command line
step. This should negate any possible barriers to entry which require manual
compilation of source code.} Scaffolder \remove{also} uses a minimal and
compact syntax to describe how \change{the}{a} genome scaffold sequence should
be generated. This syntax is simple to \change{construct}{write} and edit
whilst being succinct and readable. \change{The goal of this syntax is to make
genome scaffolds easy to write in a common text editor.}{The AGP format is
a similar format for describing scaffolds. This format can be used to define
contig order and N-filled gap regions in a scaffold. The advantages of the AGP
format is that each contig entry is defined on a single line which allows
searching the scaffold using UNIX command line tools. The scaffolder format in
comparison in contrast is written in the standardised YAML format and therefore
accessible to the many languages which provide parsers to this format. The
scaffolder format is provided with a tool explicitly to produce the fasta
sequence of scaffold specified by in the file.} \pb

@@

\subsection*{Example Use Case}

\add{The example use case for scaffolder is a combination of computation and
manual editing of a genome scaffold. As discussed many programming languages
provide libraries for reading and writing YAML. We have used scaffolder in our
genome projects create a scaffold file from parsing the output of \emph{in
silico} scaffolding tools into the scaffold file format. This scaffold was then
manually updated in a text editor with the results of using PCR to identify
gaps sequences. We see this as the advantage of describing a scaffold in both
a human and machine readable format.} \pb

>>>>

\subsection*{Comparison with other scaffold formats} %{{{2

\remove{Scaffolder was designed to be as simple to use and, assuming the Ruby
and RubyGems software are present, can be installed in a single command line
step. This should negate any possible barriers to entry which require manual
compilation of source code.} Scaffolder \remove{also} uses a minimal and
compact syntax to describe how \change{the}{a} genome scaffold sequence should
be generated. This syntax is simple to \change{construct}{write} and edit
whilst being succinct and readable. \remove{The goal of this syntax is to make
genome scaffolds easy to write in a common text editor.}

\add{AGP is a similar format for describing scaffolds. This format can be used
to define contig order and N-filled gap regions in a scaffold. The advantages
of the AGP format is that each contig entry is defined on a single line which
allows searching the scaffold using UNIX line-based tools. The scaffolder
format in comparison in contrast is written in the standardised YAML format
and therefore accessible to the many languages which provide parsers to this
format. The scaffolder format is provided with a tool explicitly to produce
the fasta sequence of scaffold specified by in the file.} \pb

@@

\subsection*{Example Use Case} %{{{2

\add{The example use case for scaffolder is a combination of computation and
manual editing of a genome scaffold. We have used scaffolder in our genome
projects to create a scaffold file from parsing the output of \emph{in silico}
scaffolding tools into the scaffold file format. This scaffold was then
manually updated in a text editor to fill gap regions with laboratory-produced
sequences.} \pb
